Model of lens candidates from Space Warps CFHTLS

### 2016-07-14 paper2.tex
removing old imgs

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

@@

We have now developed a prototype of better way to generate synthetic
images.  Figure~\figref{synthimg} illustrates.  First, areas
containing lensed images are selected (green frames in the figure).
The selected areas must contain no light from the lensing galaxy or
from extraneous objects.  Pixels within the selected areas are mapped
to a grid on the source plane, using bending angles given by the mass
model.  The mapping from lens-plane pixels to source-plane grid cells
is many-to-one, because of image multiplicity and magnification.  The
brightness of each source-plane pixel is set to the mean of all the
lens-plane pixels mapping to it.  Finally, the mapping is run back to
the lens plane.  The result is a synthetic image.  In effect, one is
reconstructing a source-plane brightness map by least-squares.

The procedure is not yet implemented in SpaghettiLens but can be
applied in post-processing.  The new synthetic images could be used to
improve the mass reconstruction, by weighting the ensemble of maps
according to how good the synthetic images are, but we have not
attempted to do so as yet.

\begin{figure}
  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
  \caption{Synthetic lensed image with source-profile fitting in SW05
    (J143454.4+522850). Top-left: original image, with areas
    containing lensed images enclosed within green frames.  Top-right:
    synthetic image (coloured arcs) with lensing galaxy and unrelated
    objects in greyscale.  Bottom from left to right: reconstructed
    source in colour, intensity (greyscale), count of lens plane
    pixels per source plane pixel, residual of original image to
    synthetic image.}
  \label{fig:synthimg}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
  \caption{
    Circularly averaged mass profile for different subsampling of central region.
    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
    }
  \label{fig:subsampling}
\end{figure}

@@

\begin{figure}
  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \caption{Model results for SW05 (J143454.4+522850).  See text in
    Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}

>>>>

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

@@

Volunteers often ask about better indicators to identify wether the
modelling resulted in a ``good'' or ``bad'' model.  We developed a
prototype of a better syntetic image than just the rendering of a
conical profile.  It operates on the composite input image.  The user
has to mask the supposed lensed images.  The algorithm then
establishes a grid on the source plane and projects the masked pixels
of the lense plane back to the source plane.  Multiple lens plane
pixels fall onto one source plane pixel and get averaged.  The new
synthetic image then reverses the mapping, coloring each pixel in the
lens plane with the corresponding values of the source plane pixel.

\begin{figure}
  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
  \caption{Synthetic image with source-profile fitting in SW05
    (J143454.4+522850). Top-left: original image; top-right: synthetic
    image (coloured arcs) with lensing galaxy and unrelated objects in
    greyscale; bottom from left to right: reconstructed source in
    colour, intensity (greyscale), count of lens plane pixels per
    source plane pixel, residual of original image to synthetic
    image.}
  \label{fig:synthimg}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_11_hires_comparison}
  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_13_hires_comparison}
  \caption{
    Circularly averaged mass profile for different subsampling of central region.
    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
    }
  \label{fig:subsampling}
\end{figure}

@@

\begin{figure}
%  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
  \caption{Model results for SW05 (J143454.4+522850).  See text in
    Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}
